Expression QTL hotspot dissection with mediation analysis and pleiotropy testing

### 2019-08-02 analysis/paper/hotspots-paper.Rmd
updated intro

---
title: "Expression QTL hotspot dissection with mediation analysis and pleiotropy testing"
author: "Frederick J. Boehm, Brian S. Yandell, and Karl W. Broman"
date: "August 1, 2019"
bibliography: research.bib
linkReferences: true
link-citations: true 
output: 
  bookdown::html_document2:
    code_folding: hide
---

>>>>

---
title: "Expression QTL hotspot dissection with mediation analysis and pleiotropy testing"
author: "Frederick J. Boehm, Brian S. Yandell, and Karl W. Broman"
date: "August 1, 2019"
bibliography: research.bib
linkReferences: true
link-citations: true 
output: 
  bookdown::html_document2: 
    code_folding: hide
  bookdown::pdf_document2:
    code_folding: none
---

### 2019-08-02 analysis/paper/intro.Rmd
updated intro
adding results text
carriage return added
started Discussion section

>>>>

@boehm2019thesis argued for complementary roles for mediation analysis and pleiotropy testing in hotspot 
dissection. Here, we clarify this argument by presenting a study of five expression trait 
hotspots in a publicly available data set. We consider each hotspot one at a time. At each hotspot, we identify 
a set of local traits that have QTL within the hotspot. We also identify a set of nonlocal traits with QTL 
arising from the hotspot. We perform pleiotropy tests and mediation analyses for all local-nonlocal trait pairs. 
Graphical summaries of our results enable us to conclude that at least one of the five hotspots is due to multiple QTL, 
while the evidence at the four other hotspots is consistent with a single local trait affecting most or all of the 
nonlocal associated traits. The Chr 5 hotspot

## INTRO IDEAS

- why is it useful to study expression hotspots? 
- why are these two methods - pleiotropy tests and mediation analyses useful for studying hotspots? 
- who else has studied hotspots? And what did they do?
